---
title: "Example Code Chunks"
author: "Joshua Langfus"
date: "2022-11-03"
output:
  pdf_document: default
  html_document:
    df_print: kable
---

```{r setup, include=FALSE}
library(tidyverse)

# import the .R file with functions to play with
source("./prorated_scoring.R")

knitr::opts_chunk$set(echo = TRUE)
```

# Sample data

```{r}
x <- c(1:9, NA, 11:19, NA)
y <- c(1:5, NA, 7:11, NA,13:20)
z <- floor(sample(rnorm(1000,mean = 10, sd = 5),20))
d <- data.frame(x,y, z)
```

# Prorated scoring

Add a new column called `score_col` to the dataframe `d` using the `score.cols.sum` function. Specify the columns across which to score with the `cols` argument -- make sure to pass a character vector of the column names as they appear in the input dataframe. Finally, in this case `n=2` and we're using mean imputation for missing values.

Use the familiar `mutate()` syntax. The trick is to use `cur_data()` as the x argument -- this passes each row of the data frame to the function.

```{r}
d %>%
  mutate(score_col = score.cols.sum(x=cur_data(),cols = c("x","y","z"), impute = "mean",n = 2))
```

Also works for the the mean with `score.cols.mean`.

```{r}
d %>%
  mutate(score_col = score.cols.mean(x=cur_data(),cols = c("x","y","z"),n = 2))
```

Each of these implements the `sum.n()` and `mean.n()` functions, respectively.


# Automatic figure making from MIRT plots

Code from the PANSS short form building project (TEOSS data)

```{r}
library(mirt)
library(ggpubr)
get_rxx <- function(mod, theta) {
  ti<-testinfo(mod, matrix(theta))
  rxx<- ti/(1+ti)
  return(data.frame(theta=theta,rxx=rxx))
}

rxx.plot <- function(mod,theta,thresh,title="Marginal Reliability") {
  # get reliabilities
  d <- get_rxx(mod,theta)
  
  # find the points where rxx is above threshold
  xx <- filter(d, rxx >= thresh)
  # grab the first and last rows as first and last points where rxx > threshold
  xx <- xx[c(1,nrow(xx)),]
  
  p <- ggplot(d, aes(x = theta, y = rxx)) +
    geom_line(linewidth = 1, alpha = .8) +
    geom_vline(xintercept = xx[1,'theta'], linetype = 5) +
    geom_vline(xintercept = xx[2,'theta'], linetype = 5) +
    geom_hline(yintercept = thresh, linetype = 2)+
    geom_text(data=xx, aes(x = theta, y = 0, label = round(theta,2)),nudge_x = .7, nudge_y = .1) +
    labs(title = title, x = expression(theta), y = expression("r"[xx]))+
    theme_classic(base_size = 12) + theme(plot.title = element_text(face = "bold",hjust = .5))
  return(p)
}


dat <- basepan30
scale.list <- list(
	"Aggression" = c("pos_p7","gps_g14"),
	"Withdrawal / Apathy" = c("neg_n2","neg_n4"),
	"Thought Disturbance" = c("pos_p2","gps_g11"),
	"Delusions & Odd Content" = c("pos_p1","gps_g9"),
	"Internalizing" = c("gps_g2","gps_g3")
)

th.lims <- c(-4, 4)
th <- seq(th.lims[1], th.lims[2], .01)

d <- scale.list %>%
	bind_rows() %>%
	pivot_longer(everything(), names_to = "Scale",values_to = "Items") %>%
	nest_by(Scale, .key = "Items") %>%
	# mutate(Items = list(Items[[,1]]))
	mutate(items = c(Items[,1])) %>%
	mutate(data  = list(basepan30[items])) %>%
	mutate(model = list(paste0(Scale,"=",paste0(items, collapse = ",")))) %>%
	mutate(grm   = list(mirt(data = data, model = model, timetype = "graded", SE = TRUE, verbose = FALSE))) %>%
	mutate(coefs = list(coef(grm, IRTpars = TRUE, simplify = TRUE, na.rm = TRUE))) %>%
	mutate(plots = list(list(
		"OCC" = plot(grm, type = "trace", main = paste0("OCC\n", Scale),
								 par.settings=simpleTheme(lty=1:4,lwd = 1),auto.key=FALSE,par.strip.text = NULL, theta_lim=th.lims),
		"rxx" = rxx.plot(grm, th, .8, paste0("Reliability\n",Scale))
			))
		)

p <- d$plots
names(p) <- d$Scale	

pl <- unlist(p, recursive = F)
```
```{r,  fig.width = 8, fig.asp = 2,warning=FALSE}
fig2 <- ggarrange(plotlist = pl,
	# p$k2agg$OCC,p$k2agg$rxx,
	# p$k2cog$OCC,p$k2cog$rxx,
	# p$k2del$OCC,p$k2del$rxx,
	# p$k2int$OCC,p$k2int$rxx,
	# p$k2wda$OCC,p$k2wda$rxx,
	widths = c(1.5,1),
	ncol = 2,
	nrow = 5)
tiff("Figure 2 GRM Upscale.tiff", width = 190, height = 450, units = 'mm', res=1000)
fig2
dev.off()
# ggexport(fig2, filename = "Figure 2 GRM Upscale.tiff", width = 5512, height = 8803)
# getwd()
```
